The impact of cosmic variance on simulating weak lensing surveys

### 2014-09-28 Writeup/paper_v3.tex
Moment based ellipticities attached

\subsection{Finding overdensities}
\label{sub:overdensities}
\begin{figure}
 \centering
  \includegraphics[width=\columnwidth]{redshift_fluxlimited}
  %\caption{\rachel{You show this figure twice.  Why?  The legend needs to say the name of the distribution, not show the functional form.}}
  \caption{Upper panel: Redshift distribution of flux-limited ($m_\text{F814W}\le 23.5$) sample with bins that are 0.05 wide. Two analytical functions with best fit parameters are plotted over it.\
           Lower panel: Plot of $(1+\delta_{g,\text{1D}}) = N/N_{\text{mod}}$ with each functional form as the model for each redshift bin.}
  \label{fig:redshift_fluxlimited}
\end{figure}

@@

Overdensity in a redshift bin is defined as the ratio of the
difference between the value given by the histogram and the value
predicted by the model to the latter:
\begin{equation}
\delta_{g,\text{1D}}=\frac{(N-N_{\text{mod}})}{N_{\text{mod}}}.  
\end{equation}
%(\rachel{This $\delta$ definition is important, so it should be in an equation environment.})
(\rachel{Call it $\delta_{g,\text{1D}}$, not $\delta$, which implies matter
  overdensity.  Better yet would be $\delta_{g,1D}$, to clearly
  indicate this is based on a 1-dimensional slice through redshift
  space rather than isolating 3D overdensities.})
We leave a 10\% margin of safety i.e. iff $\delta_{g,\text{1D}}$ from both the fits is greater than $0.1$, then we call that redshift bin as an
overdense region whereas if $\delta_{g,\text{1D}}$ from both the fits is less than $-0.1$, then we call that as an underdense region. Redshift bins with $-0.1 < \delta_{g,\text{1D}} < 0.1$ are neither too overdense
nor too underdense and we call them as `neutral regions'.

@@

We thus identify the regions $z=0.30-0.40, 0.65-0.75, 0.80-0.85$ as overdense, $z=0.55-0.65, 0.75-0.80$ as underdense and $z=0.40-0.55$ as unclassified. Although, the $z=0.40-0.55$ bin
appears to be underdense, for reasons mentioned in \S\ref{sub:volumelimiting}, we will not call them underdense.

@@

@@

When the B-band luminosity evolution is taken into account in selecting the sample, a systematic increase in the ellipticity at lower redshifts can be observed. We plot these alongside with stellar-mass selected samples, where a similar trend is found, in Fig.~\ref{fig:rms_ellip_Bband_mass}. 
Such a trend is not observed in axis ratios based on second moments.

>>>>

\subsection{Finding overdensities}
\label{sub:overdensities}
\begin{figure}
 \centering
  \includegraphics[width=\columnwidth]{redshift_fluxlimited}
  %\caption{\rachel{You show this figure twice.  Why?  The legend needs to say the name of the distribution, not show the functional form.}}
  \caption{Upper panel: Redshift distribution of flux-limited ($m_\text{F814W}\le 23.5$) sample with bins that are 0.05 wide. Two analytical functions with best fit parameters are plotted over it.\
           Lower panel: Plot of $(1+\delta_{g,\text{1D}}) = N/N_{\text{mod}}$ with each functional form as the model for each redshift bin. \arun{Give parameter values. Set minor ticks.}}
  \label{fig:redshift_fluxlimited}
\end{figure}

@@

Overdensity (as predicted by a given model) in a redshift bin is defined as the ratio of the
difference between the value given by the histogram and the value
predicted by the model to the latter:
\begin{equation}
\delta_{g,\text{1D}}=\frac{(N-N_{\text{mod}})}{N_{\text{mod}}}.  
\end{equation}
%(\rachel{This $\delta$ definition is important, so it should be in an equation environment.})
(\rachel{Call it $\delta_{g,\text{1D}}$, not $\delta$, which implies matter
  overdensity.  Better yet would be $\delta_{g,1D}$, to clearly
  indicate this is based on a 1-dimensional slice through redshift
  space rather than isolating 3D overdensities.})
Note that $\delta_{g,\text{1D}}$ is model dependent. If a model and the distribution agree, then $\delta_{g,\text{1D}}=0$ for that model at all the redshifts.

Our decision criterion is as follows. We leave a 10\% margin of safety i.e., if $\left| \delta_{g,\text{1D}} \right| < 0.1$, we say that the model and the actual distribution agree.
We label a redshift bin overdense if at least one of the models predicts the value of $\delta_{g,\text{1D}} > 0.1$ while the other predicts $\delta_{g,\text{1D}} > -0.1$, i.e.,
neutral or overdense and vice versa for the underdense regions. We label a redshift bin `neutral' if both the models predicted the value of $\delta_{g,\text{1D}}$ within the margin of safety 
\emph{or} if one of them predicts the bin to be overdense while the other predicts it to be underdense.

@@

We thus identify the regions $z=0.30-0.40, 0.65-0.75, 0.80-0.85$ as overdense, $z=0.55-0.65, 0.75-0.80$ as underdense and $z=0.40-0.55$ as unclassified. 
%Although, the $z=0.40-0.55$ bin appears to be underdense, for reasons mentioned in \S\ref{sub:volumelimiting}, we will not call them underdense.

@@

\begin{figure}
 a) \includegraphics[width=1.0\columnwidth]{rms_ellip_momentbased_noevolution.eps} \
 b) \includegraphics[width=1.0\columnwidth]{rms_ellip_momentbased_Bbandevolution_masscut.eps} \\
 \caption{RMS ellipticies with ellipticity defined as $\sqrt{e_1^2+e_2^2}$ \arun{Explain notation} \\ The horizontal errorbars simply correspond to the binwidth while the vertical ones
          are $1\sigma$ errorbars obtained by bootstrapping. The solid points correspond to the luminosity selected sample (\s$1$ sample on the left and \s$2$ sample on the right) and the unfilled
          points correspond to the sample obtained from stellar mass cuts (\s$3$). }
 \label{fig:rms_ellip_momentbased}         
\end{figure}

@@

When the B-band luminosity evolution is taken into account in selecting the sample, a systematic increase in the ellipticity at lower redshifts can be observed. We plot these alongside with stellar-mass selected samples, where a similar trend is found, in Fig.~\ref{fig:rms_ellip_Bband_mass}.

Such a trend is also observed in axis ratios based on second moments.\arun{Comment on the agreement/disagreement of the distributions themselves.} After neglecting a small number galaxies (36 galaxies between $0.3\le z<0.85$ with $\log(M/M_sun) > 10.15$)for which the moments do not converge, 
we plot the RMS ellipticites within each redshift bin in Fig.~\ref{fig:rms_ellip_momentbased}
